Supporting Information : The importance of a complete statistical description of dependence between variables for ecology and related fields

### 2019-04-12 SupportingInformation.Rmd
no change : just unique quadrats checked per plot in 1999

   # calculate shannon's index H for each plot (averaged over all Quadrates for that plot)
   x<-subset(dp,Plot==plots[i])
   x$Species<-trimws(x$Species) # to remove duplicated names of sp. (cutting white spaces) : e.g. 1999 : plot no 339
   uniq_sp<-sort(as.character(unique(x$Species)))  # These are the species in a particular plot
   Q<-as.character(unique(x$Quadrat))

   tab_each_sp<-data.frame(sp=uniq_sp,avg_cov=0,rel_avg_cov=0)
   #cat("=====================================plot : ",plots[i],"===========================\n")
   for(sp in 1:length(uniq_sp)){
    my_sp<-uniq_sp[sp]
    #cat("---------- sp = ",my_sp,"--------------------\n")
    tab_temp<-data.frame(Q=Q,abs_cov=0)
    ind<-which(x$Species==my_sp)
    li<-length(ind)
    #print(li)
    tab_temp$abs_cov[1:li]<-x$Abscover[ind]
    tab_each_sp$avg_cov[[sp]]<-mean(tab_temp$abs_cov) # avg. over Quadrats for a sp.
   }

>>>>

   # calculate shannon's index H for each plot (averaged over all Quadrates for that plot)
   x<-subset(dp,Plot==plots[i])
   x$Species<-trimws(x$Species) # to remove duplicated names of sp. (cutting white spaces) : e.g. 1999 : plot no 339
   uniq_sp<-sort(as.character(unique(x$Species)))  # These are the species in a particular plot
   Q<-as.character(unique(x$Quadrat))
   #cat("----------total unique quadrats = ",length(Q),"--------------------\n")
   tab_each_sp<-data.frame(sp=uniq_sp,avg_cov=0,rel_avg_cov=0)
   #cat("=====================================plot : ",plots[i],"===========================\n")
   for(sp in 1:length(uniq_sp)){
    my_sp<-uniq_sp[sp]
    #cat("---------- sp = ",my_sp,"--------------------\n")
    tab_temp<-data.frame(Q=Q,abs_cov=0)
    ind<-which(x$Species==my_sp)
    li<-length(ind)
    #print(li)
    tab_temp$abs_cov[1:li]<-x$Abscover[ind]
    tab_each_sp$avg_cov[[sp]]<-mean(tab_temp$abs_cov) # avg. over Quadrats for a sp.
   }
